Batch, Off-Policy, Model-free Apprencticeship Learning

### 2011-03-28 main.tex
Abstract Olivier et Matthieu

\maketitle
\begin{abstract}
We consider the IRL framework for apprenticeship learning. %1
Current IRL algorithms use a simple Monte-Carlo estimation to approximate the feature expectation of both the expert and the policy under evaluation. %2
In this paper, we propose another method for estimating the feature expectation based on the Least Square Temporal Difference (LSTD) family of algorithms. %3
This new method allows for batch, off-policy appreticeship learning in situations where the dynamics of the system remains unknown. %4
By testing it on a classical problem, we show that our method is empirically sound.%5
We also provide some theoretical results.%6
\end{abstract}
\section{Introduction}

>>>>

\maketitle
\begin{abstract}
  This paper adresses the problem of apprenticeship learning, that
  is learning control policies from demonstration by an expert. An
  efficient framework for it is inverse reinforcement learning
  (IRL). Based on the assumption that the expert maximizes a utility
  function, IRL aims at learning the reward which defines this
  utility function from example trajectories. Many IRL algorithms
  assume that the reward function is linearly parameterized and rely
  on the computation of some associated \emph{feature expectations},
  which is done through Monte Carlo simulation. However, this
  assumes to have full trajectories for the expert policy as well as
  at least a generative model for intermediate policies. In this
  paper, we introduce a temporal difference method, namely LSTD-$\mu$, to compute these
  feature expectations. This allows extending apprenticeship
  learning to a batch and off-policy setting.
\end{abstract}
\section{Introduction}
